Versioned data: why it’s needed and how it can be achieved (easily and cheaply)

### 2017-08-03 ms.tex
beginning of a discussion

Topics to consider:

\begin{itemize}

\item Addresses important need, leveraging (use) open source platforms. Shows power of open source: by writing single new package, can provide global distribution and access to data, with first class system for managing contents.
\item Versioning and open access essential for reproducibility
\item Versioning should enable better benchmarking of models, also because tests can be automated.
\item We have focussed on particular set of tools, but could do similar things with other platforms or languages.
....
\end{itemize}

@@

Because it builds on existing infra-structure for distributing software,
this system requires very little (or no) money to set up and only a
small amount of programming expertise. The current infrastructure will
not work for big or continually updated data (e.g.~weather stations or
satellite downloads). For a set of problems that need periodically
updated small-to-medium sized data (e.g.~most meta-analysis problems),
this might be a useful approach.

@@

\begin{figure}[!hb]
\centering
%\includegraphics[width=\linewidth]{figure.pdf}
\caption{Semantic versioning allows users to anticipate the types of changes that have occurred between successive versions of a dataset.
\textbf{a)} 3 numbers indicate type of change.
\textbf{b)} A typical release stream.}
\label{fig:semantic}
\end{figure}

>>>>

Many of the key roadblocks preventing a switch from a static to a dynamic data world, were technological: in the past it took great deal of money and expertise to set up a VDD system. The proliferation of cloud--based tools and open--source software have now reduced these roadblocks considerably.  We argue that by linking together the tools described above, researches can now produce, curate and distribute versioned data much more easily and cheaply than in the past.

%Topics to consider:
%
%\begin{itemize}
%
%\item Addresses important need, leveraging (use) open source platforms. Shows power of open source: by writing single new package, can provide global distribution and access to data, with first class system for managing contents.
%\item Versioning and open access essential for reproducibility
%\item Versioning should enable better benchmarking of models, also because tests can be automated.
%\item We have focussed on particular set of tools, but could do similar things with other platforms or languages.
%....
%\end{itemize}

@@

@@

\begin{figure}[!hb]
\centering
\includegraphics[width=\linewidth]{figures/Figure1.pdf}
\caption{Semantic versioning allows users to anticipate the types of changes that have occurred between successive versions of a dataset.
\textbf{a)} 3 numbers indicate type of change.
\textbf{b)} A typical release stream.}
\label{fig:semantic}
\end{figure}
